%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

% !TEX program = xelatex

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package

%
\usepackage[hidelinks]{hyperref}
\urlstyle{same}
\newcommand{\code}[1]{{\Courier \fontsize{11pt}{11pt}\selectfont #1}}
%

% --------------------  START  --------------------
\begin{document}
%
\pagestyle{empty}
%
% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna (+86) 18604511940} 
  \item {\Calluna \href{mailto:ruoyuguan.physics@gmail.com}{ruoyuguan.physics@gmail.com}}  
  \item {\Calluna \href{https://ruoyuguan.github.io/}{ruoyuguan.github.io}}  
\end{flushright}\vspace{-45pt}

\begin{flushleft}
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Ruo-Yu Guan}} %\quad {\Calluna \fontsize{14.5pt}{14.5pt}\selectfont \textsc{Ph.D.}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {School of Physics, Huazhong University of Science and Technology}{Wuhan, China}
  {Ph.D. in Physics (Theoretical Physics) \textit{(in progress)}}{Sep.\ 2025 -- Jun.\ 2029 \footnotesize{\textit{(expected)}}}
\itemListStart
\myItem{Supervisor: Prof.\ Yan Wang}
\myItem{Research Focus: gravitational-wave astrophysics (galactic double white dwarfs)}
\myItem{Affiliation: National Gravitation Laboratory (NGL), Huazhong University of Science and Technology (HUST)}
\itemListEnd

\eduHeading
  {Department of Physics, The University of Hong Kong (HKU)}{Hong Kong SAR, China}
  {M.Sc. in Physics}{Sep.\ 2023 -- Jul.\ 2024; degree conferred Nov.\ 2024}
\itemListStart
  \myItem{Supervisor: Assoc.\ Prof.\ Stephen Chi-Yung Ng}
  \myItem{Capstone Project: \textit{Identifying Sources in Cygnus OB2 Using Multiwavelength Observations}}
\itemListEnd

\eduHeading
  {Department of Materials Science, Jilin University}{Changchun, China}
  {B.Sc. in Materials Physics}{Sep.\ 2018 -- Jun.\ 2022}
\itemListStart
  \myItem{Graduation Thesis: \textit{Study on the Prompt Emission of Gamma-ray Bursts and its Polarization}}
  \myItem{Research Mentor: Prof.\ Mi-Xiang Lan (Center for Theoretical Physics and College of Physics, Jilin University)}
\itemListEnd

}

% -------------------- Work Experience --------------------
\sectionBlock{
\section{Experience}
}{
\eduHeading
  {Department of Astronomy, HUST}{Wuhan, China}
  {Research Assistant (contract)}{Nov.\ 2024 -- Jun.\ 2025}
\itemListStart
  \myItem{Supervisor: Prof.\ Yuan-Chuan Zou}
  \myItem{Gamma-ray bursts: light-curve time-series analysis and correlation studies in \code{Python}; led to a first-author peer-reviewed publication (see Publications)}
\itemListEnd

}

% -------------------- PUBLICATIONS --------------------
\sectionBlock{
\section{Publications}
}{
\pubListStart
\justifying
\item \textbf{Ruo-Yu Guan} and Mi-Xiang Lan. Interpreting time-integrated polarization data of gamma-ray burst prompt emission. \textit{Astronomy \& Astrophysics}, \textbf{670}, A160 (2023). \href{https://doi.org/10.1051/0004-6361/202243805}{doi:\allowbreak 10.1051/0004-6361/202243805}.
\item \textbf{Ruo-Yu Guan}, Fei-Fei Wang, and Yuan-Chuan Zou. Hurst index of gamma-ray burst light curves and its statistical study. \textit{Journal of High Energy Astrophysics}, \textbf{51}, 100559 (2026). \href{https://doi.org/10.1016/j.jheap.2026.100559}{doi:\allowbreak 10.1016/j.jheap.2026.100559}.
\pubListEnd
}

% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Research Projects}
}{

\projHeading
{\textbf{Galactic Structure Inference with Double White Dwarfs as Multi-Messenger Probes}}
{Ph.D. research, HUST (NGL) (Supervisor: Prof.\ Yan Wang)} {Jul.\ 2025 -- Present}

\projHeading
{\textbf{Time-Series and Correlation Analysis of Gamma-Ray Burst Light Curves}}
{Research project, HUST (Supervisor: Prof.\ Yuan-Chuan Zou); supported by National SKA Program of China (Grant No.\ 2022SKA0130100)} {Oct.\ 2024 -- Jan.\ 2026}

\projHeading
{\textbf{Gamma-Ray Burst Prompt Emission and Polarization}}
{B.Sc. research, Jilin University (Mentor: Prof.\ Mi-Xiang Lan); supported by National Natural Science Foundation of China (Grants No.\ 11903014 and 12147217)} {2022 -- Feb.\ 2023}

}

% -------------------- SKILLS --------------------

\sectionBlock{
\section{Skills}
}{
\skillListStart
\justifying
\item \emph{Languages}: Chinese (Mandarin: native; Cantonese: conversational); English (IELTS 6.5, 2023; completed an English-taught M.Sc. at HKU).
\item \emph{Programming}: \textbf{\code{Python}} (primary); \code{MATLAB}, \code{Mathematica}, \code{R}, \code{IDL}, \code{C++} (familiar).
\item \emph{Tools \& systems}: \code{NumPy}, \code{SciPy}, \code{Pandas}, \code{Matplotlib}; \code{Jupyter}; \LaTeX; \code{Git}; Windows; macOS; Linux (Ubuntu); HPC (remote Linux servers; batch jobs).
\skillListEnd
}

\end{document}